Multi-fluids for Representing Sub-filter-scale Convection

### 2020-04-03 submit2/manuscript.tex
Nearly finished responding to revier 2's annotated comments

Two vertical slice test cases are used to \change[HW]{validate}{evaluate} the \change[HW]{multi}{two}-fluid
model; a buoyant rising bubble and radiative convective equilibrium. \add[HW]{These}
are simulated at high resolution and conditionally averaged based
on the sign of the vertical velocity. The \change[HW]{multi}{two}-fluid model reproduces
the mean properties of the rising and falling fluids in \change[HW]{a single}{one} column. 
\end{abstract}

@@

\section{Introduction}

@@

\section{The Multi-fluid Boussinesq Equations}

@@

We consider dry air without turbulence so use the dynamic entrainment
described by \citeA{HC51},\citeA{AK67} and \citeA{DBF+13}:
\begin{equation}
S_{ij}=\begin{cases}
-\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
0 & \text{otherwise}
\end{cases}
\end{equation}
which is necessary to stop air in one fluid from accumulating when
vertical motion ceases (at the top of a rising plume or at the bottom
of descending air). We will also test a common form of lateral entrainment
\cite{DBF+13}:
\begin{equation}
\varepsilon=\frac{0.2}{r_{c}}
\end{equation}
where $\varepsilon$ is the well know fractional entrainment rate
and $r_{c}$ is the cloud or plume radius. Fractional entrainment is related to mass transfers by:
\begin{equation}
S_{01} = w_{1}\varepsilon.
\end{equation}

@@

The different fluids may not be well mixed so the fluid transferred
may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}.
In fact, the most buoyant air should be transferred from fluid 0 to
fluid 1 and vice versa, and the air with least downward momentum should
be transferred from 0 to 1 and vice versa. The properties of the fluids
transferred should depend on the modelling of \change[HW]{sub-grid-scale}{sub-filter-scale} variability \add[HW]{(i.e. the variability within each fluid)}
which is beyond the scope of this paper. In section \ref{sec:results}
we conditionally average high resolution solutions based on the sign
of $w$ so that $w<0$ air is in fluid 0 and $w>0$ air in fluid 1.
Therefore the air that is transferred at the interface will have $w=0$.
For two dimensional multi-fluid simulations we assume that the horizontal
velocity transferred is equal to the mean horizontal velocity of the
fluid transferred from. Therefore
\begin{equation}
\mathbf{u}_{ij}^{T}=\begin{pmatrix}u_{i}\\
v_{i}\\
0
\end{pmatrix}.
\end{equation}
For buoyancy, following \citeA{TEB19}, we use:
\begin{equation}
b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}
\end{equation}
and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
\add[HW]{
$\theta_{b}=1$ is described as an upstream approximation by \protect\citeA{Yano14} and is widely used for entrainment \protect\cite<eg.>{AK67,AS74}.
}
Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
transferred depends on the properties of the receiving fluid which
is not logical and can lead to unbounded values of $b_{i}$ in the
fluid that is loosing mass (as demonstrated in section \ref{sec:results}).

\subsection{\change[HW]{Dimensional}{Scale} Analysis\label{subsec:dimAnal}}

Dimensional analysis can guide our choice of $\gamma$ for the parameterisation of the pressure difference between fluids. We make the following assumptions
\add[HW]{in this analysis}:
\begin{enumerate}
\item The flow is buoyancy dominated.
\item The flow is close to inviscid.
\item The flow is slowly varying.
\item Fluid $i$ properties are anomalies from a neutrally stable resting
mean state 
\add[HW]{implying that the average over all fluids of $b_i$, $\mathbf{u}_i$ and $P_i$ are zero}.
\item We consider only the vertical direction where $w_{ij}^{T}=0$.
\item $P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}\approx-\gamma\nabla\cdot\mathbf{u}_{i}=-\gamma\frac{\partial w_{i}}{\partial z}$
\item There are two fluids, $i$ and $j$
\item Without loss of generality we assume that $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
and $S_{ji}=0$.
\end{enumerate}
This leads to the following balance in the momentum equation:
\begin{equation}
\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
\end{equation}
We non-dimensionalise using a length scale $L$, a buoyancy scale
$B$ and a time scale $T$ to get the non-dimensional variables:
\begin{eqnarray*}
\tilde{w} & = & w_{i}T/L\\
\tilde{b} & = & b_{i}/B\\
\tilde{z} & = & z/L.
\end{eqnarray*}
Then the non-dimensional version of (\ref{eq:wi_balances}) is:
\begin{equation}
\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
\end{equation}
The flow is buoyancy dominated so the buoyancy term should be $O(1)$
so we choose the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$
so the non-dimensional momentum equation becomes:
\begin{equation}
\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
\end{equation}
The stabilisation term must be large enough to smooth out oscillations
in $\tilde{w}$ due to advection and buoyancy but not too large to
remove all variability in $\tilde{w}$ so we need:
\begin{equation}
\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
\end{equation}

\section{Numerical \change[HW]{Solution}{Method} \label{sec:numerics}}

@@

\subsection{\add[HW]{Discrete Conditional Averaging} \label{sec:cAveraging}}

@@

\section{\change[HW]{Validation}{Evaluation} Test Cases\label{sec:results}}

@@

Including entrainment and detrainment as $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
stabilises the solution and enable the fluids to move past each other
even without pressure differences between the fluids (second row of
figure \ref{fig:multiFluidSingleColumn-bad}). However too much is
detrained from fluid 1, fluid 1 looses too much buoyancy and a discontinuity
arises at the bubble leading edge; the buoyancy force is producing
vertical motion but there is no pressure to make it smooth.

Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
and pressure difference between the fluids controlled by divergence
($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$) simulations are more
realistic (bottom three rows of figure \ref{fig:multiFluidSingleColumn-bad}).
Three values of $\gamma$ are tested. $\gamma$ is set from equation
(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
radius and a buoyancy scale equal to the initial maximum buoyancy
to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
(third row of figure \ref{fig:multiFluidSingleColumn-bad}) makes
the velocity profile too smooth and the updraft too weak so the
bubble does not rise enough. It is reasonable to consider smaller
values of $\gamma$ because the buoyancy does not retain its initial
maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
leads to the leading edge of the bubble rising too quickly. Smaller
values of $\gamma$ leave a discontinuity in the updraft velocity
at the leading edge of the bubble and larger values of $\gamma$ reduce
the velocity further, meaning that the bubble does not rise enough
(not shown). None of the values of $\gamma$ reproduce the peak updraft
velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest,
meaning that the bubble rise and $\sigma_{1}$ are approximately correct
and pressure increases above the centre of the bubble are realisitic.
The large low pressure at the bottom of the bubble is not reproduced.
This is located at the lobes of the highest buoyancy in the resolved
simulation (figure \ref{fig:bubble}). It would be tempting to model
this by assuming hydrostatic pressure or the Bernouilli equation,
but these are both forms of the momentum equation which is used to
calculate the velocity and so cannot also be used to model the pressure.

@@

The other entrainment option is the commonly used fractional entrainment
rate, $\varepsilon=0.2/r_{c}$. This is used combined with pressure
differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
This combination produces smooth solutions but the updraft is too
weak and too much is entrained into fluid 1. Using this entrainment,
the updraft will entrain more and more air until $\sigma_{1}=1$.
The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives much more accurate
entrainment and detrainment for this test case using conditional averaging
based on $w$.

Two alternative models for estimating the buoyancy of the fluid transferred
between updraft and downdraft have been tested. The results in
the fourth row if figure \ref{fig:multiFluidSingleColumn} assume
that the fluid transferred has zero buoyancy in order to keep the
positively buoyant air in fluid one and the negatively buoyant air
in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraft),
the mean buoyancy of fluid one increases. This leads to very high
buoyancy in fluid one which is not present in the resolved simulation.
The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citeA{TEB19}
so that the fluid transferred is influenced by the fluid it is moving
towards as well as where it has come from. This again leads to very
large buoyancy in fluid one and also negative buoyancy in fluid zero
which should not occur for this test case. These simple models reinforce
the idea that the buoyancy of the fluid transferred should depend
on knowledge of sub-grid-scale variability of $b$ within each fluid
\textendash{} these simple assumptions can lead to unrealistic behaviour.
The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the
fluid transferred takes the mean properties with it.

This section has demonstrated the value of using \change[HW]{single}{one} column,
multi-fluid model to simulate a buoyant rising bubble with a single
updraft fluid and a single downdraft fluid. Transfers between
the fluids have been successfully modelled using entrainment set by
divergence giving realistic updraft fractions. Entrainment calculated
as the reciprocal of plume width was not successful. The pressure
difference between the fluids has also been represented by divergence
with a coefficient close to that expected from dimensional analysis.
Including drag between the fluids did not improve simulations. Two
models of transferring non-mean properties between fluids were tested
but neither was plausible. There are clearly discrepancies between
the single-fluid resolved rising bubble and the two fluid \change[HW]{single}{one} column
rising bubble but we do not want to over fit the multi-fluid model
to one, dry, two dimensional test case.

@@

\section{Summary, Conclusions and Further Work}

This paper presents solutions of the multi-fluid Boussinesq equations
for convection, reproducing aspects of highly resolved dry convection
at coarse horizontal resolution. Two test cases are used to \change[HW]{validate}{evaluate}
the multi-fluid model. The first is a Boussinesq version of the well
known two dimensional dry rising bubble of \citeA{BF02} and the second
is a dry two dimensional version of radiative-convective equilibrium
with heating at the ground and uniform radiative cooling. High resolution
single-fluid simulations are conditionally averaged based on the sign
of vertical velocity ($w$) in order to create rising and falling
fluids which each have their own mean buoyancy, velocity and pressure.
The two-fluid, \change[HW]{single}{one} column Boussinesq model reproduces mean vertical
heat and mass transport of these test cases.

@@

Conditionally averaging the high resolution solutions based on $w$
leads to convecting and non-convecting regions with area fractions,
$\sigma_{i}$, which are approximately uniform with height. Models
for entrainment and detrainment into and out of convecting regions
must clearly be consistent with the definition of the convecting region.
We propose a model for entrainment and detrainment based on divergence
that leads to excellent agreement with $\sigma$ from the high resolution
solutions. We also test a more conventional fractional entrainment
rate based on the reciprocal of the plume width which leads to unrealistic
convecting area fractions.

A set of unknowns in the multi-fluid equations are the properties
of the fluid that are transferred from one fluid to another. An obvious
first guess would be that fluid takes its mean buoyancy and velocity
with it when it is transferred. However sub-grid-scale variability
of each fluid means that we expect that the most buoyant fluid will
be transferred to the rising fluid or the fluid with the largest vertical
velocity will be transferred to the rising fluid and vice versa. An
accurate estimate of these would depend on knowledge of the sub-grid-scale
variability of each fluid which we do not have. Instead we assume
that the fluid transferred in each direction has zero vertical velocity
which is consistent with our conditional averaging. We have tested
three models for the buoyancy of the fluid transferred. The most successful
is to assume that the fluid takes its mean buoyancy with it. Assuming
that the buoyancy of the transferred fluid is an average of the buoyancy
of both fluids can lead to unrealistically large or small, unbounded
buoyancies. Similarly, if we assume that one fluid has negative buoyancy
and the other positive buoyancy and we transfer fluid of zero buoyancy,
then unbounded buoyancy can occur. A better model of the buoyancy
of the fluid transferred would rely on more information the sub-grid-scale
variability.

>>>>

Two vertical slice test cases are \change[HW]{used}{developed} to \add[HW]{tune parameters and to} \change[HW]{validate}{evaluate} the \change[HW]{multi}{use of two}-fluid
\change[HW]{model}{equations to represent dry, two-dimensional, sub-grid-scale convection}; a buoyant rising bubble and radiative convective equilibrium. \add[HW]{These}
are \add[HW]{first} simulated at high resolution and conditionally averaged based
on the sign of the vertical velocity \add[HW]{and next simulated with the two-fluid model in one vertical column}. The \change[HW]{multi}{two}-fluid model reproduces
the mean properties of the rising and falling fluids in \change[HW]{a single}{one} column. 
\end{abstract}

@@

\section{Introduction \label{sec:intro}}

@@

\section{The Multi-fluid Boussinesq Equations \label{sec:multiBouEqns}}

@@

\add[HW]{The transfers between fluids are related to entrainment, $\varepsilon$, and detrainment, $\delta$. Fluid 0 is the environment and fluid 1 is updrafts implying:}
\begin{equation}
S_{01} = w_1\varepsilon, \;\;\;\;\;\;\;
S_{10} = w_0\delta.
\end{equation}
\add[HW]{Results using two formulations of entrainment are presented in section \protect\ref{sec:results}. The first is}
\remove[HW]{We consider dry air without turbulence so use}
the dynamic entrainment described by
\citeA{HC51}, \citeA{AK67} and \citeA{DBF+13}:
\begin{equation}
S_{ij}=\begin{cases}
-\nabla\cdot\mathbf{u}_{i} & \text{if }\nabla\cdot\mathbf{u}_{i}<0\\
0 & \text{otherwise.}
\end{cases}
\end{equation}
\change[HW]{which is necessary to stop air in}{This formulation prevents} one fluid from accumulating when vertical motion ceases (at the top of a rising plume or at the bottom of descending air). \remove[HW]{We will also test a}{A} common form of lateral entrainment \cite<eg.>{DBF+13} \add[HW]{is also tested in section \protect\ref{sec:results}}:
\begin{equation}
\varepsilon=\frac{0.2}{r_{c}}
\end{equation}
where $r_{c}$ is the cloud or plume radius. 
\remove[HW]{Fractional entrainment is related to mass transfers by:}

@@

\change[HW]{The different}{Each} fluid may not be well mixed so the fluid transferred
may not have the mean properties of the fluid it is leaving \cite<as was assumed by>{WM19}. In fact, 
\change[HW]
{the most buoyant air should be transferred from fluid 0 to
fluid 1 and vice versa, and the air with least downward momentum}
{since we are conditionally averaging based on the vertical velocity, $w$, the sub-set of fluid 0 that is accelerating and about to be rising}
should be transferred from 0 to 1 and vice versa.
\change[HW]{The properties of the fluids transferred should depend on the modelling of sub-grid-scale variability which}
{A realistic estimate of the properties of the fluid transferred can only be made based on knowledge of sub-filter-scale variability (i.e. the variability within each fluid). Modelling of sub-filter-scale variability}
is beyond the scope of this paper.
%
In section \ref{sec:results}
we conditionally average high resolution solutions based on the sign
of $w$ so that $w<0$ air is in fluid 0 and $w>0$ air in fluid 1.
Therefore the air that is transferred at the interface will have $w=0$.
For two dimensional multi-fluid simulations we assume that the horizontal
velocity transferred is equal to the mean horizontal velocity of the
fluid transferred from. Therefore
\begin{equation}
\mathbf{u}_{ij}^{T}=\begin{pmatrix}u_{i}\\
v_{i}\\
0
\end{pmatrix}.
\end{equation}
For buoyancy, following \citeA{TEB19}, we use:
\begin{equation}
b_{ij}^{T}=\theta_{b}b_{i}+(1-\theta_{b})b_{j}
\end{equation}
and present results using $\theta_{b}=\frac{1}{2}$ and $\theta_{b}=1$.
\add[HW]{
$\theta_{b}=1$ is described as an upstream approximation by \protect\citeA{Yano14} and is widely used for entrainment \protect\cite<eg.>{AK67,AS74}.
}
Note that $\theta_{b}\ne1$ implies that the buoyancy of the fluid
transferred depends on the properties of the receiving fluid which
is not logical and can lead to unbounded values of $b_{i}$ in the
fluid that is loosing mass (as demonstrated in section \ref{sec:results}).

\subsection{\label{subsec:dimAnal}\change[HW]{Dimensional}{Scale}
 Analysis}

Dimensional analysis can guide our choice of $\gamma$ for the parameterisation of the pressure difference between fluids. We make the following assumptions
\add[HW]{in this analysis}:
\begin{enumerate}
\item The flow is buoyancy dominated.
\item The flow is close to inviscid.
\item The flow is slowly varying.
\item Fluid $i$ properties are anomalies from a neutrally stable resting
mean state 
\add[HW]{implying that the average over all fluids of $b_i$, $\mathbf{u}_i$ and $P_i$ are zero}.
\item We consider only the vertical direction where $w_{ij}^{T}=0$.
\item $P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}\approx-\gamma\nabla\cdot\mathbf{u}_{i}=-\gamma\frac{\partial w_{i}}{\partial z}$
\item There are two fluids, \change[HW]{$i$ and $j$}{0 and 1.}
\item Without loss of generality we assume that $S_{ij}=-\frac{\partial w_{i}}{\partial z}>0$
and $S_{ji}=0$.
\end{enumerate}
\change[HW]{This leads to the following balance in the momentum equation}{These assumptions can be used to simplify the multi-fluid $w$ equation, (\protect\ref{eq:mom})}:
\begin{equation}
\frac{\partial w_{i}^{2}}{\partial z}-\gamma\frac{\partial^{2}w_{i}}{\partial z^{2}}=b_{i}\label{eq:wi_balances}
\end{equation}
We non-dimensionalise using a length scale $L$, a buoyancy scale
$B$ and a time scale $T$ to get the non-dimensional variables:
\begin{eqnarray*}
\tilde{w} & = & w_{i}T/L\\
\tilde{b} & = & b_{i}/B\\
\tilde{z} & = & z/L.
\end{eqnarray*}
Then the non-dimensional version of (\ref{eq:wi_balances}) is:
\begin{equation}
\underbrace{{\frac{L}{T^{2}}\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{TL}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{B\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDomTmp}
\end{equation}
The flow is buoyancy dominated so the buoyancy term should be $O(1)$
so we choose the scaling $B=L/T^{2}\implies T=(L/B)^{\frac{1}{2}}$
so the non-dimensional momentum equation becomes:
\begin{equation}
\underbrace{{\frac{\partial\tilde{w}^{2}}{\partial\tilde{z}}}}_{\text{advection}}-\underbrace{{\frac{\gamma}{B^{\frac{1}{2}}L^{\frac{3}{2}}}\frac{\partial^{2}\tilde{w}}{\partial\tilde{z}^{2}}}}_{\text{stabilisation}}=\underbrace{\tilde{b}}_{\text{buoyancy}}.\label{eq:wi_nonDom-1}
\end{equation}
The stabilisation term must be large enough to smooth out oscillations
in $\tilde{w}$ due to advection and buoyancy but not too large to
remove all variability in $\tilde{w}$. \change[HW]{so we need}{Therefore the stabilisation term should be $O(1)$ which implies that}:
\begin{equation}
\gamma\sim B^{\frac{1}{2}}L^{\frac{3}{2}}.\label{eq:gammaDimAnal}
\end{equation}
\add[HW]{This will be used to guide the choice of $\gamma$ in section \protect\ref{sec:results}.}
\section{\label{sec:numerics}Numerical \change[HW]{Solution}{Method}}

@@

\subsection{\label{sec:cAveraging}\add[HW]{Discrete Conditional Averaging} }

@@

\section{\label{sec:results}\change[HW]{Validation}{Evaluation} Test Cases}

@@

Including entrainment and detrainment as $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$
stabilises the solution and enable the fluids to move past each other
even without pressure differences between the fluids (second row of
figure \ref{fig:multiFluidSingleColumn-bad}). However too much is
detrained from fluid 1, fluid 1 loses too much buoyancy and a discontinuity
arises at the bubble leading edge; the buoyancy force is producing
vertical motion but there is no pressure to make it smooth.

Using entrainment and detrainment set by divergence ($S_{ij}=-\nabla\cdot\mathbf{u}_{i}$)
and pressure difference between the fluids controlled by divergence
($P_{i}=P-\gamma\nabla\cdot\mathbf{u}_{i}$), \add[HW]{the} simulations are more
realistic (bottom three rows of figure \ref{fig:multiFluidSingleColumn-bad}).
Three values of $\gamma$ are tested. $\gamma$ is set from equation
(\ref{eq:gammaDimAnal}) using a length scale equal to the bubble
radius and a buoyancy scale equal to the initial maximum buoyancy
to give $\gamma=2.3\times10^{4}\text{m}^{2}\text{s}^{-1}$. This $\gamma$
(third row of figure \ref{fig:multiFluidSingleColumn-bad}) makes
the velocity profile too smooth and the updraft too weak so the
bubble does not rise enough. It is reasonable to consider smaller
values of $\gamma$ because the buoyancy does not retain its initial
maximum for very long. Using $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$
gives more accurate solutions whereas using $\gamma=4\times10^{3}\text{m}^{2}\text{s}^{-1}$
leads to the leading edge of the bubble rising too quickly. Smaller
values of $\gamma$ leave a discontinuity in the updraft velocity
at the leading edge of the bubble and larger values of $\gamma$ reduce
the velocity further, meaning that the bubble does not rise enough
(not shown). None of the values of $\gamma$ reproduce the peak updraft
velocities but $\gamma=10^{4}\text{m}^{2}\text{s}^{-1}$ comes closest,
meaning that the bubble rise and $\sigma_{1}$ are approximately correct
and pressure increases above the centre of the bubble are realisitic.
The large low pressure at the bottom of the bubble is not reproduced.
This is located at the lobes of the highest buoyancy in the resolved
simulation (figure \ref{fig:bubble}). It would be tempting to model
this by assuming hydrostatic pressure or the Bernouilli equation,
but these are both forms of the momentum equation which is used to
calculate the velocity and so cannot also be used to model the pressure.

@@

The other entrainment option is the commonly used fractional entrainment
rate, $\varepsilon=0.2/r_{c}$. This is used \change[HW]{combined}{in combination with} with pressure
differences between fluids in the middle row of figure \ref{fig:multiFluidSingleColumn-bad}.
This combination produces smooth solutions but the updraft is too
weak and too much is entrained into fluid 1. Using this entrainment,
the updraft will entrain more and more air until $\sigma_{1}=1$.
The $S_{ij}=-\nabla\cdot\mathbf{u}_{i}$ model gives
\change[HW]{much more accurate entrainment and detrainment for this test case using conditional averaging based on $w$.}
{results closer to the reference solution conditionally averaged based on $w$.}

Two alternative models for estimating the buoyancy of the fluid transferred
between updraft and downdraft have been tested. The results in
the fourth row \change[HW]{if}{of} figure \ref{fig:multiFluidSingleColumn} assume
that the fluid transferred has zero buoyancy in order to keep the
positively buoyant air in fluid one and the negatively buoyant air
in fluid 0. Thus when zero buoyancy air leaves fluid one (the updraft),
the mean buoyancy of fluid one increases. This leads to very high
buoyancy in fluid one which is not present in the resolved simulation.
The results in the bottom row of figure \ref{fig:multiFluidSingleColumn}
use $b_{ij}^{T}=\frac{1}{2}\left(b_{0}+b_{1}\right)$ following \citeA{TEB19}
so that the fluid transferred is influenced by the fluid it is moving
towards as well as where it has come from. This again leads to very
large buoyancy in fluid one and also negative buoyancy in fluid zero
which \change[HW]{should not occurfor this test case.}{does not occur in the conditionally averaged reference solution.} These simple models reinforce
the idea that the buoyancy of the fluid transferred should depend
on knowledge of \change[HW]{sub-grid-scale}{sub-filter-scale} variability of $b$ within each fluid
\textendash{} these simple assumptions can lead to unrealistic behaviour.
The best model tested is $b_{ij}^{T}=b_{i}$ which assumes that the
fluid transferred takes the mean properties with it. \add[HW]{Modelling of higher-order moments of variability within each fluid is an area of active research.}

This section has demonstrated the \change[HW]{value of using}{plausible utility of} \change[HW]{single column, multi-}{a two-}fluid model to simulate a \add[HW]{sub-grid-scale} buoyant rising bubble with a single
updraft fluid and a single downdraft fluid. Transfers between
the fluids have been \remove[HW]{successfully} modelled using entrainment set by divergence giving \remove[HW]{realistic} updraft fractions \add[HW]{close to the conditionally averaged reference solution}. Entrainment calculated
as the reciprocal of plume width was not successful. The pressure
difference between the fluids has also been represented by divergence
with a coefficient close to that expected from dimensional analysis.
Including drag between the fluids did not improve simulations. Two
models of transferring non-mean properties between fluids were tested
but neither was plausible. There are clearly discrepancies between
the single-fluid resolved rising bubble and the two fluid \change[HW]{single}{one} column
rising bubble but we do not want to over fit the multi-fluid model
to one, dry, two dimensional test case.

\add[HW]{Using the lessons learned from modelling the rising bubble, a statistically stationary case with many plumes is simulated next.}

@@

\section{Summary, Conclusions and Further Work \label{sec:concs}}

\change[HW}{This paper presents solutions of the multi-fluid Boussinesq equations for convection, reproducing aspects of highly resolved dry convection
at coarse horizontal resolution.}
{This paper presents solutions of the two-fluid Boussinesq equations using coarse horizontal resolution (one column) which reproduce aspects of highly resolved single-fluid simulations of dry, two-dimensional convection.}
Two test cases are used to \change[HW]{validate}{evaluate}
the multi-fluid model. The first is a Boussinesq version of the well
known two dimensional dry rising bubble of \citeA{BF02} and the second
is a dry two dimensional version of radiative-convective equilibrium
with heating at the ground and uniform radiative cooling. High resolution
single-fluid simulations are coditionally averaged based on the sign
of vertical velocity ($w$) in order to \change[HW]{create}{define} rising and falling
fluids which each have their own mean buoyancy, velocity and pressure.
The two-fluid, \change[HW]{single}{one} column Boussinesq model reproduces mean vertical
heat and mass transport of these test cases.

@@

Conditionally averaging the high resolution solutions based on $w$
leads to convecting and non-convecting regions with area fractions,
$\sigma_{i}$, which are approximately uniform with height. Models
for entrainment and detrainment into and out of convecting regions
\change[HW]{must clearly}{need to} be consistent with the definition of the convecting region.
\change[HW]{We propose a}{A} model for entrainment and detrainment based on divergence \add[HW]{is proposed}
that leads to excellent agreement with $\sigma$ from the high resolution
solutions. \change[HW]{We also test a}{A} more conventional fractional entrainment rate based on the reciprocal of the plume width \add[HW]{is also tested} which leads to unrealistic convecting area fractions.

\change{A set of unknowns in the multi-fluid equations are the}{The} properties of the fluid that are transferred from one fluid to another \add[HW]{are unknowns in the multi-fluid equations that require closure}. An obvious
first guess would be that fluid takes its mean buoyancy and velocity
with it when it is transferred. However sub-\change{grid}{filter}-scale variability
of each fluid means that we expect that the most buoyant fluid will
be transferred to the rising fluid or the fluid with the largest vertical
velocity will be transferred to the rising fluid and vice versa. An
accurate estimate of these would depend on knowledge of the sub-grid-scale
variability of each fluid which we do not have. Instead we assume
that the fluid transferred in each direction has zero vertical velocity
which is consistent with our conditional averaging. We have tested
three models for the buoyancy of the fluid transferred. The most successful
is to assume that the fluid takes its mean buoyancy with it. Assuming
that the buoyancy of the transferred fluid is an average of the buoyancy
of both fluids can lead to unrealistically large or small, unbounded
buoyancies. Similarly, if we assume that one fluid has negative buoyancy
and the other positive buoyancy and we transfer fluid of zero buoyancy,
then unbounded buoyancy can occur. A better model of the buoyancy
of the fluid transferred would rely on more information the sub-grid-scale
variability.
